# Alpha rarefaction

```{r, include=FALSE}
# at some point this should be moved into bookdown
source("~/Desktop/hpcbio-git/hergenrother-16S-mouse-2022Sept/src/common_code.R", local = knitr::knit_global())
```

```{r}
physeq.filtered <- readRDS('./results/physeq.filtered.RDS')
```

Let's check whether we're adequately capturing diversity.  This is a simple alpha rarefaction curve; here we want to see the number of taxa plateau as the counts increase.

```{r, include=FALSE}
p <- suppressMessages(ranacapa::ggrare(physeq.filtered, step = 1000,
           # color = "Treatment",
           # label = "Label",
            se = FALSE,
            plot = FALSE,
            )) + ggtitle("Alpha Rarefaction") +
  scale_color_manual(values = dittoSeq::dittoColors()) +
  scale_linetype_manual(values = c( "dashed", "dotted","twodash", "solid")) +
  geom_line(aes(linetype = Treatment, color = Treatment)) +
  theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) +
 # guides(fill=guide_legend(override.aes=list(color=dittoSeq::dittoColors(), linetype = c( "dashed", "dotted","twodash", "solid"))))
#guides(colour = guide_legend(override.aes = list(color=dittoSeq::dittoColors(), linetype = c( "dashed", "dotted","twodash", "solid"))))
  labs(color  = "Key", linetype = "Key")

# Remove first line layer (made by ggrare)
p <- delete_layers(p, idx = 1L)

ggsave("alpha-rarefaction-colorByTreatment_CBF.pdf", path = "./results/final-plots", width = 8, height = 5, device = "pdf")
```


We can also split this by Treatment:

```{r}
p <- p + facet_wrap(~Treatment) + ggtitle("Alpha Rarefaction by Treatment")

ggplotly(p)
ggsave("alpha-rarefaction-splitByTreatment.pdf", path = "./results/final-plots", device = "pdf")
```

Rarefaction looks pretty decent. There may be a few samples that didn't plateau (not all diversity seems to have been captured)


And also by Day (w/ legend):

```{r}
p <- p + facet_wrap(~Day) + ggtitle("Alpha Rarefaction by Day") 

ggplotly(p)
ggsave("alpha-rarefaction-splitByDay_CBF.pdf", path = "./results/final-plots", device = "pdf", width = 6, height = 4)
```
And also by Day (w/o legend):

```{r}
p <- p + facet_wrap(~Day) + ggtitle("Alpha Rarefaction by Day") +
  theme(legend.position="none")

ggplotly(p)
ggsave("alpha-rarefaction-splitByDay_CBF_nolegend.pdf", path = "./results/final-plots", device = "pdf", width = 5, height = 4)
```
